---
title: "Stock Portfolio"
author: "linda"
date: "10/15/2020"
output: html_document

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  message = FALSE, 
  warning = FALSE, 
  tidy=FALSE,     # display code as typed
  size="small")   # slightly smaller font for code
options(digits = 3)

# default figure size
knitr::opts_chunk$set(
  fig.width=6.75, 
  fig.height=6.75,
  fig.align = "center"
)
```

```{r load-libraries, warning=FALSE, message=FALSE, echo=FALSE}
library(tidyverse)  # Load ggplot2, dplyr, and all the other tidyverse packages
library(mosaic)
library(ggthemes)
library(lubridate)
library(fivethirtyeight)
library(here)
library(skimr)
library(janitor)
library(vroom)
library(tidyquant)
library(rvest)    # scrape websites
library(purrr)  
library(lubridate) #to handle dates
```

# My Portfolio

I am an investor in China A-share stock market. Here is my portfolio consisting of seven stocks diversifying in industries.
```{r}
myStocks <- c("600519.SS", "601398.SS", "601318.SS", "601857.SS", "603288.SS", 
              "600276.SS","600048.SS","000001.SS" ) %>% 
  tq_get(get = "stock.prices", 
         from = "2018-01-01",
         to = "2020-10-14") %>%
  group_by(symbol)
  
glimpse(myStocks)

name <- data.frame(name = c("Moutai", "ICBC", "PingAn ", "China Petroleum", "Haitian", "Hengrui","Poly","SSE Composite Index"), 
                   symbol = c("600519.SS", "601398.SS", "601318.SS", "601857.SS", "603288.SS", "600276.SS","600048.SS","000001.SS"))

name$name <- factor(name$name, 
                    levels = name$name,
                    ordered = TRUE)

myStocks <- myStocks %>% 
  left_join(name)
```

# Individual Stock Performance

I started my investment since 2018. Let's take a look how the seven stocks and the index performed in the past three years.

```{r}
myStocks %>% 
  ggplot(aes(x = date, y = close)) +
  geom_line() +
  facet_wrap(~name, scales = "free") +
  labs(title = "Price Performance of my seven stocks and SSE Composite index ",
       subtitle = "from 2018.1.1 to 2020.10.14",
       x = "",
       y = "price") +
  theme_bw()
```

# Returns of the stocks

```{r}
#calculate daily returns
myStocks_returns_daily <- myStocks %>%
  tq_transmute(select     = adjusted, 
               mutate_fun = periodReturn, 
               period     = "daily", 
               type       = "log",
               col_rename = "daily_returns",
               cols = c(nested.col))  %>% 
  left_join(name)

#calculate monthly  returns
myStocks_returns_monthly <- myStocks %>%
  tq_transmute(select     = adjusted, 
               mutate_fun = periodReturn, 
               period     = "monthly", 
               type       = "arithmetic",
               col_rename = "monthly_returns",
               cols = c(nested.col)) %>% 
  left_join(name)

#calculate yearly returns
myStocks_returns_annual <- myStocks %>%
  group_by(symbol) %>%
  tq_transmute(select     = adjusted, 
               mutate_fun = periodReturn, 
               period     = "yearly", 
               type       = "arithmetic",
               col_rename = "yearly_returns",
               cols = c(nested.col))%>% 
  left_join(name)
```
Moutai in 2019 gave me the largest yearly return among all the stocks I hold.

plot my monthly returns
```{r}
ggplot(myStocks_returns_monthly, aes(x=monthly_returns))+
  geom_density()+
  facet_wrap(~name)+
  theme_bw()+
  labs(x="Monthly Returns", 
       y="Density", 
       title = "Distribution of Monthly Returns")
```

median of my monthly returns
```{r}
myStocks_returns_monthly %>% 
  group_by(name) %>% 
  mutate(median_monthly_returns = median(monthly_returns)) %>% 
  ggplot(aes(x = monthly_returns, y = reorder(name, median_monthly_returns),color = name)) +
  geom_boxplot() +
  labs(title = "boxplot of monthly median return",
       subtitle = "from 2018.1.1 to 2020.10.14",
       x = "monthly return",
       y = "stocks") +
  scale_x_continuous(labels = scales::percent_format()) +
  guides(color=FALSE) + 
  theme_bw() 
```

Moutai seems to give me the largest median monthly return among the seven stocks I hold.

# Risks of my portfolio

Risk Return plot
```{r}
stocks_risk_return <- myStocks_returns_monthly %>% 
  tq_performance(Ra = monthly_returns, Rb = NULL, performance_fun = table.Stats) %>% 
  select(symbol,ArithmeticMean, GeometricMean, Minimum,Maximum,Stdev, Quartile1, Quartile3) %>% 
  left_join(name)
stocks_risk_return %>% 
  ggplot(aes(x = Stdev, y = ArithmeticMean, color = name, label = name)) +
  geom_point(size = 4) +
  labs(title = "Risk-return Profile",
       subtitle = "from 2018.1.1 to 2020.10.14",
       x = "Risk (stdev of monthly returns)",
       y = "Average monthly return") +
  scale_x_continuous(labels = scales::percent) +
  scale_y_continuous(labels = scales::percent) +
  geom_text(hjust = "inward", vjust = "inward") +
  theme_bw() +
  theme(legend.position = "none", plot.margin = unit(c(0.2,0.2,0.2,0.2), "inches"))
```
Haitian has the largest risk using standard deviation as measurement. China Petroleum gave me negative returns.

Stock correlation
```{r}
table_capm_returns <- myStocks_returns_monthly[-1] %>%
            pivot_wider(names_from = "name",
                        values_from = "monthly_returns")  

table_capm_returns[-1] %>% 
  GGally::ggpairs() +
  theme_bw()+
    theme(axis.text.x = element_text(angle = 90, size=8),
         axis.title.x = element_blank())
```
Haitian has lower correltaion with other six stocks. Although the stock has high volatility, it offered good diversification effect to my portfolio.
